Sparse Function-space Representation of Neural Networks

### 2023-09-05 workshops/icml-duality/main.tex
fixed typos

%Need for adaptive learning methods + failures with current methods
Given an approximate inference technique, we demonstrate that NNs emit `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2023memory}.
In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, our parameterization captures
information from {\em all} data points in a sparse representation, essential for scaling to deep learning data sets.
% predictive uncertainty.
Importantly, the dual parameterization can be used to 1) sparsify the GP without requiring further optimization
(e.g. variational inference) whilst capturing information from all data points, and 2) can incorporate new data without retraining (in a computationally efficient manner
by conditioning on new data).
% In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, our parameterization captures information from {\em all} data points in a sparse representation, essential for predictive uncertainty.
% Importantly, our method predicts in the same space as the original trained NN, with the benefit of avoiding the
% complexity introduced by working in weight-space and the notorious cubic complexity of vanilla GPs.
%\todo{Could make it clearer that the GP predicts in the output space while avoiding the NN parameter space}
%, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
Through the dual parameterization, we establish a connection between the NN, GPs, and sparse approximations similar to sparse variational GPs~\citep{titsias2009variational}. We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained NN; see \cref{fig:teaser} for an example. %Moreover, this dual parameterization can be exploited to perform dual conditioning \citep{chang2022fantasizing}, \ie, an effective approach for conditioning on new data without needing to retrain the model (see \cref{fig:teaser}).
%As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}) \todo{Effective compared to what?}.
\looseness-2

@@

We consider supervised learning with inputs $\vx_i \in \inputDomain$ and outputs $\vy_i \in \outputDomain$ (e.g. regression) or $\vy_{i} \in \{0,1\}^{C}$ (e.g. classification),
giving a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$.
We introduce a  NN $f_\mathbf{w}: \inputDomain \to \outputDomain$ with weights $\weights \in \R^{P}$ and use a likelihood function $p(\vy \mid f_\mathbf{w}(\vx))$
to link the function values to the output $\vy$ (e.g. Categorical for classification).
For notational conciseness we stick to scalar outputs $y_{i}$.

@@

% \subsection{Laplace approximation}
\textbf{MAP}
It is common to train NN weights $\vw$ to minimize the (regularized) empirical risk,
%
\begin{align} \label{eq-empirical-risk}
  \weights^{*} &=
                 \arg \min_{\weights} \mathcal{L}(\dataset,\weights) \nonumber \\
               &=
  \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \underbrace{\ell(f_\weights(\mathbf{x}_{i}), y_i)}_{-\log p(y_{i} \mid f_{\vw}(\vx_{i}))} + \underbrace{\delta \mathcal{R}(\weights)}_{-\log p(\vw)}.
\end{align}
%
This objective corresponds to the log joint distribution $\mathcal{L}(\mathcal{D},\vw)=p(\mathcal{D}, \vw)$
as the loss can be interpreted as a negative log likelihood $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y_{i} \mid f_\weights(\vx_{i}))$
and the regularizer corresponds to a log prior over the weights $\delta\mathcal{R}(\weights) = -\log p(\vw)$.
For example, a weight decay regularizer $\mathcal{R}(\vw) = \frac{1}{2}\|\weights\|^{2}_2$ corresponds to a Gaussian prior over the weights $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$, with
prior precision $\delta$.
As such, we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution.

@@

% \textbf{Weight space GLM is equivalent to a GP}
\textbf{Gaussian processes}
As Gaussian distributions remain tractable under linear transformations, we can covert the linear model from
weight space to function space \citep[see Ch.~2.1 in ][]{rasmussen2006gaussian}.
 % highlighted that the GGN approximation corresponds to a local linearization of the NN,
As such (and shown in \citet{immer2021improving}), the Bayesian GLM in \cref{eq-glm} has an equivalent GP formulation,
% \begin{align}
%   p_{\text{\sc GP}}(\vy \mid \vx, \mathcal{D}) &= \E_{q(\vf)} \left[ p(\vy \mid \vf)\right] %\nonumber \\
%   % &\approx \frac{1}{S} \sum_{s} p(\vy \mid f_{\vw_{s}}^{\text{lin}}(\vx)), \quad \vw_{s} \sim q(\vw)
% \end{align}
% where the GP posterior is given by,
% \begin{subequations}  \label{eq-gp-pred-immer}
% \begin{align}
%   p_{\text{\sc GP}}(\vy \mid \vx, \mathcal{D}) &= \E_{q(\vf)} \left[ p(\vy \mid \vf)\right] \\ %\nonumber \\
%   \myexpect_{p(f_i \mid\vy)}[f_i] &= f_{\vw^{*}}(\vx_{i}), \\
%   \mathrm{Var}_{p(f_i \mid \vy)}[f_i] &= k_{ii} - \vk_{\vx i}^\top ( \MKxx + \bm\Lambda^{-1})^{-1} \vk_{\vx i},
% \end{align}
% \end{subequations}
\begin{align} \label{eq-gp-pred-immer}
  p_{\text{\sc GP}}(y_{i} \mid \vx, \mathcal{D}) &= \E_{q(f_{i})} \left[ p(y_{i} \mid f_{i} )\right]
\end{align}
where $q(f_{i}) = \mathcal{N} \left( f_{\vw^{*}}(\vx_{i}), \sigma^{2}_{i} \right)$ is the GP's predictive posterior with variance,
% where $q(\vf) = \mathcal{N} \left( \myexpect_{p(f_i \mid\vy)}[f_i], \mathrm{Var}_{p(f_i \mid \vy)}[f_i] \right)$ is the predictive GP posterior given by,
\begin{align} \label{eq-gp-pred-immer-gp}
  % \myexpect_{p(f_i \mid\vy)}[f_i] &= f_{\vw^{*}}(\vx_{i}), \\
  \sigma^{2}_{i} &= k_{ii} - \vk_{\vx i}^\top ( \MKxx + \bm\Lambda^{-1})^{-1} \vk_{\vx i},
\end{align}
where the kernel $\kappa(\vx,\vx')=\frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'}$ is the Neural Tangent Kernel \citep[NTK,][]{jacot2018neural}
and $f_i = f_\vw(\vx_i)$ is the function output at $\vx_i$.
The $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where
each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, $k_{ii} = \kappa(\vx_i, \vx_i)$ and $\bm\Lambda = - \nabla^2_{\vf \vf}\log p(\vy \mid \vf)$ can be interpreted as per-input noise.
% For notational conciseness, we % \cref{eq-laplace-approx-function-space},
% restrict our notatin to a single function output. The extension to multiple outputs is straightforward.

@@

Not only does the GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer}) struggle to scale to large
data sets but it also cannot incorporate new data by conditioning on it.
This is because it's posterior mean is the NN  $f_{\vw^*}(\vx)$.
Our method overcomes both of these limitations via a dual parameterization.
Importantly, our dual parameterization enables us to 1) sparsify the GP without further optimization, and 2)
incorporate new data without retraining.\looseness-1 % (in a computationally efficient manner).

@@

\begin{figure*}[t]
  % \centering\scriptsize
  \centering\small
  % \setlength{\figurewidth}{.18\textwidth}
  \setlength{\figurewidth}{.27\textwidth}
  \setlength{\figureheight}{\figurewidth}
  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\Large},y tick label style={font=\LARGE},title style={yshift=-4pt,font=\LARGE}, y label style={font=\LARGE},x label style={font=\LARGE},grid=major, width=\figurewidth, height=\figureheight}
  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
  \pgfplotsset{xlabel={$M$ as \% of $N$},ylabel style={yshift=-5pt},xlabel style={yshift=-5pt}}
  %
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \pgfplotsset{ylabel=NLPD}
    \input{./fig/australian.tex}
  \end{minipage}
  \hfill
  % \begin{minipage}[t]{.12\textwidth}
  %   \raggedleft
  %   \input{./fig/breast_cancer.tex}
  % \end{minipage}
  % \hfill
  % \begin{minipage}[t]{.12\textwidth}
  %   \raggedleft
  %   \input{./fig/ionosphere.tex}
  % \end{minipage}
  % \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/glass.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/vehicle.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/waveform.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/digits.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/satellite.tex}
  \end{minipage}\\[-1em]
  %
  % Legend
  \definecolor{steelblue31119180}{RGB}{31,119,180}
  \definecolor{darkorange25512714}{RGB}{255,127,14}
  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean\textcolor{gray}{\footnotesize$\pm$std} over 5 seeds) on UCI classification tasks: \our (\myline{steelblue31119180}) vs. GP subset (\myline{darkorange25512714}). Our \our converges fast for all cases showing clear benefits of its ability to summarize all the data onto a sparse set of inducing points. The number of inducing points $M$ are specified as a percent of the number of training data $N$.}
  \label{fig:uci}
  %\vspace*{-6pt}
\end{figure*}

@@

We highlight that \our differs from the GP subset method from \citet{immer2021improving}, which results in several advantages.
First, \our leverages a dual parameterization to construct a sparse GP, which captures information from the entire data set.
In contrast, \citet{immer2021improving} utilise a subset of the data points which ignores information from the rest of the data set.
% It is also worth noting that our sparsification via dual parameters does not require any further optimization, we do not need to retrain a separate sparse GP.
Second, \our makes predictions with the GP mean, whereas \citet{immer2021improving} center predictions around NN predictions $f_{\vw^*}(\cdot)$.
As such, \our can incorporate new data without retraining (i.e. condition on new data) whilst the GP subset method cannot.

@@

%
We evaluate \our on eight UCI~\citep{UCI} binary and multi-class classification tasks.
% Following \citet{immer2021improving}, we used a two-layer MLP with width 50 and tanh activation functions and we used half of the test data set as a validation data set.
Following \citet{immer2021improving}, we used a two-layer MLP with width 50, tanh activation functions and a
$70\%\ (\text{train}):15\%\ (\text{validation}) :15\%\ (\text{test})$ data split.
We trained the NN using Adam \cite{adam} with a learning rate of $10^{-4}$ and a batch size of $128$.
Training was stopped when the validation NLPD stopped decreasing after 1000 steps.
The checkpoint with lowest NLPD was the NN MAP.
Each experiment was run for $5$ seeds.\looseness-1

% We first compare \our to other posthoc Bayesian deep learning approaches.
% In particular, we compare to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM).
We first compare \our to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM) in \cref{eq-glm}.
We use the Laplace PyTorch library \citep{daxberger2021laplace} with the full Hessian.%, i.e. we do not resort to the diagonal or KFAC approximations.
It is common practice to tune the prior precision $\delta$ after training the NN.
That is, find a prior precision $\delta_{\text{tune}}$ which has a better NLPD on the validation set than the $\delta$ used to train the NN.
Note that this leads to different prior precisions being used for training and inference.
We highlighted that technically this invalidates the Laplace/SFR methods as the NN weights are no longer the MAP weights.
Nevertheless, we report results when the prior precision $\delta$ is tuned (\cref{tbl:uci} right) and is not tuned (\cref{tbl:uci} left).
When tuning the prior precision $\delta$, \our matches the performance of the Laplace methods (BNN/GLM).
Interestingly, \our also  performs well without tuning the prior precision $\delta$, unlike the Laplace methods (BNN/GLM).

>>>>

%Need for adaptive learning methods + failures with current methods
Given an approximate inference technique, we demonstrate that NNs emit `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2023memory}.
In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, our parameterization captures
information from {\em all} data points in a sparse representation, essential for scaling to deep learning data sets.
% predictive uncertainty.
Importantly, the dual parameterization can be used to 1) sparsify the GP without requiring further optimization
(e.g. variational inference) whilst capturing information from all data points, and 2) incorporate new data without retraining (in a computationally efficient manner
by conditioning on new data).
% In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, our parameterization captures information from {\em all} data points in a sparse representation, essential for predictive uncertainty.
% Importantly, our method predicts in the same space as the original trained NN, with the benefit of avoiding the
% complexity introduced by working in weight-space and the notorious cubic complexity of vanilla GPs.
%\todo{Could make it clearer that the GP predicts in the output space while avoiding the NN parameter space}
%, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
Through the dual parameterization, we establish a connection between the NN, GPs, and sparse approximations similar to sparse variational GPs~\citep{titsias2009variational}. We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained NN; see \cref{fig:teaser} for an example. %Moreover, this dual parameterization can be exploited to perform dual conditioning \citep{chang2022fantasizing}, \ie, an effective approach for conditioning on new data without needing to retrain the model (see \cref{fig:teaser}).
%As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}) \todo{Effective compared to what?}.
\looseness-2

@@

We consider supervised learning with inputs $\vx_i \in \inputDomain$ and outputs $\vy_i \in \outputDomain$ (e.g. regression) or $\vy_{i} \in \{0,1\}^{C}$ (e.g. classification),
giving a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$.
We introduce a  NN $f_\mathbf{w}: \inputDomain \to \outputDomain$ with weights $\weights \in \R^{P}$ and use a likelihood function $p(\vy \mid f_\mathbf{w}(\vx))$
to link the function values to the output $\vy$ (e.g. Categorical for classification).
For notational conciseness, we stick to scalar outputs $y_{i}$.

@@

% \subsection{Laplace approximation}
\textbf{MAP}
It is common to train NN weights $\vw$ to minimize the (regularized) empirical risk,
%
\begin{align} \label{eq-empirical-risk}
  \weights^{*} &=
                 \arg \min_{\weights} \mathcal{L}(\dataset,\weights) \nonumber \\
               &=
  \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \underbrace{\ell(f_\weights(\mathbf{x}_{i}), y_i)}_{-\log p(y_{i} \mid f_{\vw}(\vx_{i}))} + \underbrace{\delta \mathcal{R}(\weights)}_{-\log p(\vw)}.
\end{align}
%
This objective corresponds to the log joint distribution $\mathcal{L}(\mathcal{D},\vw)=p(\mathcal{D}, \vw)$
as the loss can be interpreted as a negative log-likelihood $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y_{i} \mid f_\weights(\vx_{i}))$
and the regularizer corresponds to a log prior over the weights $\delta\mathcal{R}(\weights) = -\log p(\vw)$.
For example, a weight decay regularizer $\mathcal{R}(\vw) = \frac{1}{2}\|\weights\|^{2}_2$ corresponds to a Gaussian prior over the weights $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$, with
prior precision $\delta$.
As such, we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution.

@@

% \textbf{Weight space GLM is equivalent to a GP}
\textbf{Gaussian processes}
As Gaussian distributions remain tractable under linear transformations, we can convert the linear model from
weight space to function space \citep[see Ch.~2.1 in ][]{rasmussen2006gaussian}.
 % highlighted that the GGN approximation corresponds to a local linearization of the NN,
As such (and shown in \citet{immer2021improving}), the Bayesian GLM in \cref{eq-glm} has an equivalent GP formulation,
% \begin{align}
%   p_{\text{\sc GP}}(\vy \mid \vx, \mathcal{D}) &= \E_{q(\vf)} \left[ p(\vy \mid \vf)\right] %\nonumber \\
%   % &\approx \frac{1}{S} \sum_{s} p(\vy \mid f_{\vw_{s}}^{\text{lin}}(\vx)), \quad \vw_{s} \sim q(\vw)
% \end{align}
% where the GP posterior is given by,
% \begin{subequations}  \label{eq-gp-pred-immer}
% \begin{align}
%   p_{\text{\sc GP}}(\vy \mid \vx, \mathcal{D}) &= \E_{q(\vf)} \left[ p(\vy \mid \vf)\right] \\ %\nonumber \\
%   \myexpect_{p(f_i \mid\vy)}[f_i] &= f_{\vw^{*}}(\vx_{i}), \\
%   \mathrm{Var}_{p(f_i \mid \vy)}[f_i] &= k_{ii} - \vk_{\vx i}^\top ( \MKxx + \bm\Lambda^{-1})^{-1} \vk_{\vx i},
% \end{align}
% \end{subequations}
\begin{align} \label{eq-gp-pred-immer}
  p_{\text{\sc GP}}(y_{i} \mid \vx, \mathcal{D}) &= \E_{q(f_{i})} \left[ p(y_{i} \mid f_{i} )\right]
\end{align}
where $q(f_{i}) = \mathcal{N} \left( f_{\vw^{*}}(\vx_{i}), \sigma^{2}_{i} \right)$ is the GP's predictive posterior with variance,
% where $q(\vf) = \mathcal{N} \left( \myexpect_{p(f_i \mid\vy)}[f_i], \mathrm{Var}_{p(f_i \mid \vy)}[f_i] \right)$ is the predictive GP posterior given by,
\begin{align} \label{eq-gp-pred-immer-gp}
  % \myexpect_{p(f_i \mid\vy)}[f_i] &= f_{\vw^{*}}(\vx_{i}), \\
  \sigma^{2}_{i} &= k_{ii} - \vk_{\vx i}^\top ( \MKxx + \bm\Lambda^{-1})^{-1} \vk_{\vx i},
\end{align}
where the kernel $\kappa(\vx,\vx')=\frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'}$ is the Neural Tangent Kernel \citep[NTK,][]{jacot2018neural}
and $f_i = f_\vw(\vx_i)$ is the function output at $\vx_i$.
The $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where
each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, $k_{ii} = \kappa(\vx_i, \vx_i)$ and $\bm\Lambda = - \nabla^2_{\vf \vf}\log p(\vy \mid \vf)$ can be interpreted as per-input noise.
% For notational conciseness, we % \cref{eq-laplace-approx-function-space},
% restrict our notatin to a single function output. The extension to multiple outputs is straightforward.

@@

Not only does the GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer}) struggle to scale to large
data sets but it also cannot incorporate new data by conditioning on it.
This is because its posterior mean is the NN  $f_{\vw^*}(\vx)$.
Our method overcomes both of these limitations via a dual parameterization.
Importantly, our dual parameterization enables us to 1) sparsify the GP without further optimization, and 2)
incorporate new data without retraining.\looseness-1 % (in a computationally efficient manner).

@@

\begin{figure*}[t]
  % \centering\scriptsize
  \centering\small
  % \setlength{\figurewidth}{.18\textwidth}
  \setlength{\figurewidth}{.27\textwidth}
  \setlength{\figureheight}{\figurewidth}
  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\Large},y tick label style={font=\LARGE},title style={yshift=-4pt,font=\LARGE}, y label style={font=\LARGE},x label style={font=\LARGE},grid=major, width=\figurewidth, height=\figureheight}
  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
  \pgfplotsset{xlabel={$M$ as \% of $N$},ylabel style={yshift=-5pt},xlabel style={yshift=-5pt}}
  %
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \pgfplotsset{ylabel=NLPD}
    \input{./fig/australian.tex}
  \end{minipage}
  \hfill
  % \begin{minipage}[t]{.12\textwidth}
  %   \raggedleft
  %   \input{./fig/breast_cancer.tex}
  % \end{minipage}
  % \hfill
  % \begin{minipage}[t]{.12\textwidth}
  %   \raggedleft
  %   \input{./fig/ionosphere.tex}
  % \end{minipage}
  % \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/glass.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/vehicle.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/waveform.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/digits.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/satellite.tex}
  \end{minipage}\\[-1em]
  %
  % Legend
  \definecolor{steelblue31119180}{RGB}{31,119,180}
  \definecolor{darkorange25512714}{RGB}{255,127,14}
  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean\textcolor{gray}{\footnotesize$\pm$std} over 5 seeds) on UCI classification tasks: \our (\myline{steelblue31119180}) vs. GP subset (\myline{darkorange25512714}). Our \our converges fast for all cases showing clear benefits of its ability to summarize all the data onto a sparse set of inducing points. The number of inducing points $M$ are specified as a percentage of the number of training data $N$.}
  \label{fig:uci}
  %\vspace*{-6pt}
\end{figure*}

@@

We highlight that \our differs from the GP subset method from \citet{immer2021improving}, which results in several advantages.
First, \our leverages a dual parameterization to construct a sparse GP, which captures information from the entire data set.
In contrast, \citet{immer2021improving} utilize a subset of the data points which ignores information from the rest of the data set.
% It is also worth noting that our sparsification via dual parameters does not require any further optimization, we do not need to retrain a separate sparse GP.
Second, \our makes predictions with the GP mean, whereas \citet{immer2021improving} center predictions around NN predictions $f_{\vw^*}(\cdot)$.
As such, \our can incorporate new data without retraining (i.e. condition on new data) whilst the GP subset method cannot.

@@

%
We evaluate \our on eight UCI~\citep{UCI} binary and multi-class classification tasks.
% Following \citet{immer2021improving}, we used a two-layer MLP with width 50 and tanh activation functions and we used half of the test data set as a validation data set.
Following \citet{immer2021improving}, we used a two-layer MLP with width 50, tanh activation functions and a
$70\%\ (\text{train}):15\%\ (\text{validation}) :15\%\ (\text{test})$ data split.
We trained the NN using Adam \cite{adam} with a learning rate of $10^{-4}$ and a batch size of $128$.
Training was stopped when the validation NLPD stopped decreasing after 1000 steps.
The checkpoint with the lowest NLPD was the NN MAP.
Each experiment was run for $5$ seeds.\looseness-1

% We first compare \our to other posthoc Bayesian deep learning approaches.
% In particular, we compare to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM).
We first compare \our to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM) in \cref{eq-glm}.
We use the Laplace PyTorch library \citep{daxberger2021laplace} with the full Hessian.%, i.e. we do not resort to the diagonal or KFAC approximations.
It is common practice to tune the prior precision $\delta$ after training the NN.
That is, find a prior precision $\delta_{\text{tune}}$ which has a better NLPD on the validation set than the $\delta$ used to train the NN.
Note that this leads to a different prior precision being used for training and inference.
We highlighted that technically this invalidates the Laplace/SFR methods as the NN weights are no longer the MAP weights.
Nevertheless, we report results when the prior precision $\delta$ is tuned (\cref{tbl:uci} right) and is not tuned (\cref{tbl:uci} left).
When tuning the prior precision $\delta$, \our matches the performance of the Laplace methods (BNN/GLM).
Interestingly, \our also  performs well without tuning the prior precision $\delta$, unlike the Laplace methods (BNN/GLM).
